\bf The forestecology R package for fitting and assessing models of interspecies competitive effects on the growth of trees

### 2021-02-23 paper/forestecology.Rmd
missed on thing

The `forestecology` package has the following ecological goals: 1) to evaluate the effect of competitor species identity on using permutation tests and 2) to evaluate model performance using spatial cross-validation. To achieve these goals, we outline a basic analysis sequence comprising of these four main steps:

>>>>

The `forestecology` package has the following ecological goals: 1) to evaluate the effect of competitor species identity using permutation tests and 2) to evaluate model performance using spatial cross-validation. To achieve these goals, we outline a basic analysis sequence comprising of these four main steps:

### 2021-02-23 paper/forestecology.tex
missed on thing

The \texttt{forestecology} package has the following ecological goals:
1) to evaluate the effect of competitor species identity on using
permutation tests and 2) to evaluate model performance using spatial
cross-validation. To achieve these goals, we outline a basic analysis
sequence comprising of these four main steps:

@@

We then compare the observed and fitted/predicted growths to compute the
root mean squared error (RMSE) of our model fit. DAVE NOTE: I rounded
all the RMSEs, in ecology convention to not show WAY more digits than
resolution of hte measurement.

>>>>

The \texttt{forestecology} package has the following ecological goals:
1) to evaluate the effect of competitor species identity using
permutation tests and 2) to evaluate model performance using spatial
cross-validation. To achieve these goals, we outline a basic analysis
sequence comprising of these four main steps:

@@

We then compare the observed and fitted/predicted growths to compute the
root mean squared error (RMSE) of our model fit. DAVE NOTE: I rounded
all the RMSEs, in ecology convention to not show WAY more digits than
resolution of the measurement.
